\subsection*{Banana Pancakes\index{Banana Pancakes}   \hrulefill { \small Jack Johnson}}
\addcontentsline{toc}{subsection}{Banana Pancakes}
\begin{guitar}
  \begin{multicols}2{}
%\begin{multicols}{2}
Well can't you see that it's just r[am]aining?
There ain't no need to go [G]outside.
But [D7]Baby!



You h[G]ardly even kn[D7]ow this
when [Am]i try to sh[C7]ow you
S[G]ong is meant to k[D7]eep you
from d[Am]oing what you're supp[C7]osed to
w[G]akin' up to [D7]early
m[am]aybe we could sl[C7]eep
m[G]ake you banana p[D7]ancakes
pr[am]etend like its th[C7]e weekend
n[Am]ow



we could pretend it all the t[G]ime.
Can't you see that its just r[Am]aining.
Ain't no need to go [G]outside.
But just m[D7]aybe!



Hala ka ukulele, 
mama made a baby.
Really don't mind to practice 
cause you're my little lady.
Lady lady love me 
cause I love to lay you lazy.
We could close the curtains 
pretend like theres no world
outside.



Then we could pretend it all the time.
cant you see that its just raining,
Ain't no need to go outside.



\\
Ain't no need Ain't no need.
mmmm  mmmm  mmmmm  mmmmm
Can't you see can't you see?
Rain all day and I don't mind.

\columnbreak


But the t[Am]elephones singin ringin 
its too early dont pick it [D]up.
We don't need to
we got [Am]everything we need right here 
and everything we need is en[D]ough.
just so easy


When the wh[Bm]ole world fits inside of your arms
do we r[Em]eally need to pay attention to the [C]alarm?
wake up sl[G]ow,  mmmmm m[D]mmmmm
wake up sl[G]ow



But Baby!

You hardly even know this
when i try to show you
Song is meant to keep you 
from doing what you're supposed to.


Wakin' up to early
maybe we could sleep
make you banana pancakes
pretend like its the weekend


now



We could pretend it all the time.
cant you see that its just raining.
Ain't no need to go outside
aint no need aint no need.
Rain all day and I really really really don't mind.
Can't you see can't you see?
you gotta wake up slow

%\end{multicols}
\end{multicols}
\end{guitar}
