\subsection*{Sunny\index{Sunny}   \hrulefill { \small Bobby Hebb}}
\addcontentsline{toc}{subsection}{Sunny}
\begin{guitar}
[Em]Sunny, [G]yesterday my [C]life was filled with [F#m(5-/7)]rain. $\quad$ $\quad$ [B7] $\quad$
[Em]Sunny, [G]you smiled at me and [C]really eased the [F#m(5-/7)]pain. $\quad$ $\quad$ [B7] $\quad$
Oh, the [Em]dark days are done and the [G]bright days are here,
[C]my sunny one shines [F]so sincere.
Oh, [F#m(5-/7)]Sunny one so [B7]true, I love [Em]you.

Sunny, thank you for the sunshine bouquet.
Sunny, thank you for the love you brought my way.
You gave to me your all and all,
now I feel ten feet tall.
Oh, Sunny one so true, I love you.

[Fm]Sunny, [Ab]thank you for the [Db]truth you've let me [Gm(5-/7)]see. $\quad$ $\quad$ [C7] $\quad$
[Fm]Sunny, [Ab]thank you for the [Db]facts from A to [Gm(5-/7)]Z. $\quad$ $\quad$ [C7]  $\quad$
[Fm]My life was torn like [Ab]a windblown sand,
then [Db]a rock was formed when [F#]we held hands.
[Gb(5-/7)]Sunny one so [C7]true, I love [Fm]you.

[F#m]Sunny, [A]thank you for that [D]smile upon your [G#m(5-/7)]face. $\quad$ $\quad$ [C#7] $\quad$
[F#m]Sunny, [A]thank you for that [D]gleam that flows with [G#m(5-/7)]grace. $\quad$ $\quad$ [C#7] $\quad$
[F#m]You're my spark of [A]nature's fire,
[D]you're my sweet [G]complete desire.
[G#m(5-/7)]Sunny one so [C#7]true, I love [F#m]you.

[Gm]Sunny, [Bb]yesterday my [Eb]life was filled with [Am(5-/7)]rain. $\quad$ $\quad$ [D7] $\quad$
[Gm]Sunny, [Bb]you smiled at me and [Eb]really eased the [Am(5-7)]pain. $\quad$ $\quad$ [D7] $\quad$
Oh, the [Gm]dark days are done and the [Bb]bright days are here,
[Eb]my sunny one shines [Ab]so sincere.
Oh, [Am(5-/7)]Sunny one so [D7]true, I love [Gm]you.
\end{guitar}
