\subsection*{Learn to fly\index{Learn to fly}   \hrulefill { \small Foo Fighters}}
\addcontentsline{toc}{subsection}{Learn to fly}
\begin{guitar}
Intro: \chords{B|F\#m|E} (2x)
R[B]un and tell all of the a[F#m]ngels
T[E]his could take all night
T[B]hink I need a devil to h[F#m]elp me get things r[E]ight
H[B]ook me up a new evolut[F#m]ion
Cause t[E]his one is a lie
We s[B]at around laughing, and w[F#m]atching the last one d[E]ie



Now l[B]ooking to the sky to s[F#m]ave me
L[E]ooking for a sign of life
L[B]ooking for something to h[F#m]elp me burn out b[E]right
I'[B]m looking for a complic[F#m]ation
L[E]ooking to the tide of light
M[G]ake my way back h[A]ome and learn to f[B]ly

\chords{B|F\#m|E}(2x)
Think I'm done nursing patients,
It could wait one night.
Give it all away if you give me one last try
We live happily ever trapped in future save my life.
Run and tell the angels that everything's alright.



I'm l[B]ooking to the sky to s[F#m]ave me,
L[E]ooking for a sign of light.
L[B]ooking for something to h[F#m]elp me burnout b[E]right.
I'm l[B]ooking for a compli[F#m]cation,
L[E]ooking for some time to try.
M[G]ake my way back h[A]ome when I learn to f[E]ly.
M[G]ake my way back h[A]ome when I learn to f[B]ly....
....a[G]long with me I c[D]an't quite make it a[E]lone.
T[G]ry to make this l[A]ife my own.
F[B]ly.....a[G]long with me I c[D]an't quite make it a[E]lone.
T[G]ry to make this l[A]ife my own.
I'm l[B]ooking to the sky to s[F#m]ave me,
L[E]ooking for a sign of life.
L[B]ooking for something to h[F#m]elp me burnout b[E]right.
I'm l[B]ooking for a compl[F#m]ication,
L[E]ooking for some time to try.
M[G]ake my way back h[A]ome when I learn to
L[B]ooking to the sky to s[F#m]ave me,
L[E]ooking for a sign of life.
L[B]ooking for something to h[F#m]elp me burnout b[E]right.
\end{guitar}
