\subsection*{New Jersey Story\index{New Jersey Story}   \hrulefill { \small Vic Ruggiero}}
\addcontentsline{toc}{subsection}{New Jersey Story}
\begin{guitar}
Well, J[G]ohnny and the neighbors talk about fire
O[C]utside the old front door
My g[H]irl says ''Please, would you put down the phone?''
And st[C]amps her feet for m[G]ore


Bobby's in the fridge, lookin' pensive, he says,
''My, your beer looks expensive!
''You don't even drink it, man
''Who'd you buy it for?''


And I said, ''Wh[E]at you gonna do when your dreams come true? H[A]uh?''
Well, you pr[C]obably won't have n[D]othin' more to s[G]ay
''Wh[E]at you gonna do when your dreams come true 
if I m[A]ake your dream come true for you?
''W[C]ill you tell me th[D]at you'll go aw[G]ay?''


See, I look like a poet and I don't even know it
'Til somebody tells me so
They say, ''Hey Tom Sawyer, how's your lawyer?''
I said, ''Rich, far as I know''


They say, ''Hey Hem the Wayman, what do you say?
''Why you look so glum for?''
I said, ''The basket and the dryer never line up right
''And all my clean clothes fall on the floor''


And I said, ''What you gonna do when your dreams come true? Huh?''
Well, you probably won't have nothin' more to say
''What you gonna do when your dreams come true 
if I make your dream come true for you?
''Will you tell me that you'll go away?''


Y'know I found a genie in a lamp when the weather was damp
In nineteen eighty-four
But I put it on a shelf and I kept it to myself
'Cause I didn't know what to wish for


In nineteen ninety-nine, the weather was fine
And they said the world was gonna end
So I rubbed that lamp and I made a little wish
And we all woke up again


And I said, ''What you gonna do when your dreams come true? Huh?''
Well, you probably won't have nothin' more to say
''What you gonna do when your dreams come true 
if I make your dream come true for you?
''Will you tell me that you'll go away?''


''If I make your dream come true for you today?
''Honey, if I make your dream come true for you today?
''Oh, if I make your dream come true for you today?'' 
\end{guitar}
