\subsection*{Walk on the wild side\index{Walk on the wild side}   \hrulefill { \small Lou Reed}}
\addcontentsline{toc}{subsection}{Walk on the wild side}
\begin{guitar}

[C]Holly came from Miami, [Fmaj7]FLA
[C]Hitch-hiked her way across the [Fmaj7]USA
[C]Plucked her eyebrows [D]on the way
[F]Shaved her legs and then [D]he was a she
She says, [C]Hey babe,
Take a [Fmaj7]walk on the wild side.
She said, [C]Hey honey,
Take a walk on the [Fmaj7]wild side.

Candy came from out on the Island
In the backroom she was everybody's darlin'
But she never lost her head
Even when she was giving head
She says, Hey babe,
Take a walk on the wild side.
Said, Hey babe,
Take a walk on the wild side.
And the colored girls go:
Doo do doo do doo do do doo, ...

Little Joe never once gave it away
Everybody had to pay and pay
A hustle here and a hustle there
New York City's the place where they said, Hey babe,
Take a walk on the wild side.
I said, Hey Joe,
Take a walk on the wild side.

Sugar Plum Fairy came and hit the streets
Lookin' for soul food and a place to eat
Went to the Apollo
You should've seen 'em go, go, go
They said, Hey sugar,
Take a walk on the wild side.
I said, Hey babe,
Take a walk on the wild side.
All right, huh

Jackie is just speeding away
Thought she was James Dean for a day
Then I guess she had to crash
Valium would have helped that bash
She said, Hey babe,
Take a walk on the wild side.
I said, Hey honey,
Take a walk on the wild side.
And the colored girls say:
Doo do doo do doo do do doo....
\end{guitar}
