\subsection*{Mister Moon\index{Mister Moon}   \hrulefill { \small Mando Diao}}
\addcontentsline{toc}{subsection}{Mister Moon}
\begin{guitar}
[Bm] [A] [G] [E]


[Bm]Mr [A]Moon,[G] Mr Moon maybe [E]your time is coming
[Bm]Mr [A]Moon, Mr [G]Moon what's happening [E]in the room?
[Bm]We’ll search our [A]hearts before you [G]die, let the [E]times fade away.
[Bm]It was [A]given as a p[G]romise to each and [E]every man.

[D]I wanna love you but i’m [A]growing old
[Bm]Ten little soldiers screaming [G]in my soul.
[D]Will she come over when it’s [A]time to go,
[Bm]come on and show me little [G]drummerboy,
[E]no Mr [G]Moon, [E]Mr [G]Moon, Mr [F#]Moon[G]  [F#] [F#] [G] [F#]  [F#] [G] [F#] [G]


Sad but true, sad but true
You’re telling me what to do
I’ve learned my lesson, that stupid question
Now it hurts my pride
And you’re a girl, a serious girl
Showing me the world
Oh my love, you’re so tired
But you must think quiet


I wanna love you but i’m growing old
Ten little soldiers screaming in my soul.
Will she come over when it’s time to go,
come on and show me little
drummerboy, no
Mr Moon, Mr Moon, Mr Moon.
Hey, hey, heeey…..
Mr Moon, Mr Moon, Mr Moon.


I wanna love you but i’m growing old
Ten little soldiers screaming in my soul.
Will she come over when it’s time to go, come on and show me little
drummerboy.


I wanna love you but i’m growing old
Ten little soldiers screaming in my soul.
The day is using up it's final breath
I've never been so sure I've never doubted you,
Mr Moon, Mr Moon, Mr Moon
\end{guitar}
