\subsection*{The Mercy Seat\index{Mercy Seat}   \hrulefill { \small Johnny Cash}}
\addcontentsline{toc}{subsection}{The Mercy Seat}
\begin{guitar}
  \begin{multicols}{2}
\chords{Am|Em|Am|Em}

It all began when they took me from my home
And put me on Death Row,
a crime for which I am totally innocent, you know.

I began to warm and chill
To objects and their fields,
A ragged cup, a twisted mop
The face of Jesus in my soup
Those sinister dinner deals
The meal trolley's wicked wheels
A hooked bone rising from my food
All things either good or ungood.

[Am]And the mercy seat is waiting
[Am#7]And I think my head is burning
[Am7]And in a way I'm yearning
To be [G]done with all this weighing of the [Gm]truth.
An eye for an eye
And a tooth for a [bB]tooth
And anyway I told the [F]truth
And I'm not afraid to [Am]die.

{\scriptsize Am \hspace{0.5cm} Em \hspace{0,5cm} Am \hspace{0.5cm} Em \hspace{0,5cm}}

[Am]I hear stories from the [Am#7]chamber
Christ was born into a [Am7]manger
And like some ragged stranger
He [G]died upon the cross
Might I [Gm]say, it seems so fitting in its [bB]way
He was a carpenter by [F]trade
Or at least that's what I'm [Am]told

{\scriptsize Am \hspace{0.5cm} Em \hspace{0,5cm} Am \hspace{0.5cm} Em \hspace{0,5cm}}

My kill-hand's
tatooed E.V.I.L. across it's brother's fist
That filthy five! They did nothing to challenge or resist.

[Am]In Heaven His throne is made of [Am#7]gold
The ark of his Testament is [Am7]stowed
A throne from which I'm told
All [G]history does unfold.
It's [Gm]made of wood and wire
And my [bB]body is on fire
[F]And God is never far [Am]away.

\columnbreak
Into the mercy seat I climb
My head is shaved, my head is wired
And like a moth that tries
To enter the bright eye
I go shuffling out of life
Just to hide in death awhile
And anyway I never lied.

And the mercy seat is waiting
And I think my head is burning
And in a way I'm yearning
To be done with all this weighing of the truth.
An eye for an eye
And a tooth for a tooth
And anyway I told the truth
And I'm not afraid to die

And the mercy seat is burning
And I think my head is glowing
And in a way I'm hopin'
to be done with all this twistin' of the truth.
An eye for an eye
And a tooth for a tooth
And any way there was no proof
And I'm not afraid to die

And the mercy seat is glowing
And I think my head is smoking
And in a way I'm hopin'
to be done with all these looks of disbelief.
A life for a life
And a truth for a truth
And I've got nothin' left to loose.
And I'm not afraid to die

And the mercy seat is smoking
And I think my head is melting
And in a way that's helpin'
to be done with all this twistin' of the truth
An eye for an eye
And a tooth for a tooth
And any way I told the truth
But I'm afraid I told a lie.
\end{multicols}
\end{guitar}
